The ChEMBL database as Linked Open Data

### 2012-05-01 article.tex
Cleaned up author lines, fixing some whitespace issues

\author{
  Egon L Willighagen$^{1}$% // FIXED FIRST AUTHOR
  \email{Egon L Willighagen - egon.willighagen@maastrichtuniversity.nl}
\and
  Andra Waagmeester$^1$%
  \email{Andra Waagmeester - FIXME}
\and
  Ola Spjuth$^2$%
  \email{Ola Spjuth - FIXME}
\and
  Peter Ansell$^3$%
  \email{Peter Ansell - FIXME}
\and
  Antony Williams$^4$%
  \email{Antony Williams - FIXME}
\and
  Valery Tkachenko$^4$%
  \email{Valery Tkachenko - FIXME}
\and
  Janna Hastings$^5$%
  \email{Janna Hastings - FIXME}
\and
  John Overington$^6$%
  \email{John Overington - FIXME}
\and
  Anna Gaulton$^6$%
  \email{Anna Gaulton - FIXME}
\and
  Mark Davies$^6$%
  \email{Mark Davies - FIXME}
\and
  Bin Chen$^7$%
  \email{Bin Chen - FIXME}
\and
  David Wild$^7$%
  \email{David Wild - FIXME}
}

\address{
    \iid(1)Department of Bioinformatics - BiGCaT, Maastricht University, P.O. Box 616, UNS50 Box 19, NL-6200 MD, Maastricht, The Netherlands  \\
    \iid(2)Department of Pharmaceutical Biosciences, Uppsala University, PO Box 591, SE-751 24, Uppsala, Sweden \\
    \iid(3)University of Queensland, St Lucia, Qld 4072, Australia \\
    \iid(4)Royal Society of Chemistry, 904 Tamaras Circle, Wake Forest, NC 27587, U.S.A. \\
    \iid(5)Chemoinformatics and Metabolism, European Bioinformatics Institute, POSTAL CODE, Hinxton, United Kingdom \\
    \iid(6)EMBL-European Bioinformatics Institute, Wellcome Trust Genome Campus, Hinxton, Cambridgeshire, CB10 1SD, United Kingdom \\ 
    \iid(7)School of Informatics and Computing, Indiana University, Bloomington, IN, U.S.A.
}

>>>>

\author{Egon~L.~Willighagen$^{1}$\email{Egon~L.~Willighagen - egon.willighagen@maastrichtuniversity.nl}\and
Andra~Waagmeester$^1$\email{Andra Waagmeester - FIXME}\and
Ola Spjuth$^2$\email{Ola Spjuth - FIXME}\and
Peter~Ansell$^3$\email{Peter Ansell - FIXME}\and
Antony~Williams$^4$\email{Antony Williams - FIXME}\and
Valery~Tkachenko$^4$\email{Valery Tkachenko - FIXME}\and
Janna~Hastings$^5$\email{Janna Hastings - FIXME}\and
John~Overington$^6$\email{John Overington - FIXME}\and
Anna~Gaulton$^6$\email{Anna Gaulton - FIXME}\and
Mark~Davies$^6$\email{Mark Davies - FIXME}\and
Bin~Chen$^7$\email{Bin Chen - FIXME}\and
David~Wild$^7$\email{David Wild - FIXME}
}

\address{\iid(1)Department of Bioinformatics - BiGCaT, Maastricht University, P.O. Box 616, UNS50 Box 19, NL-6200 MD, Maastricht, The Netherlands  \\
\iid(2)Department of Pharmaceutical Biosciences, Uppsala University, PO Box 591, SE-751 24, Uppsala, Sweden \\
\iid(3)University of Queensland, St Lucia, Qld 4072, Australia \\
\iid(4)Royal Society of Chemistry, 904 Tamaras Circle, Wake Forest, NC 27587, U.S.A. \\
\iid(5)Chemoinformatics and Metabolism, European Bioinformatics Institute, POSTAL CODE, Hinxton, United Kingdom \\
\iid(6)EMBL-European Bioinformatics Institute, Wellcome Trust Genome Campus, Hinxton, Cambridgeshire, CB10 1SD, United Kingdom \\ 
\iid(7)School of Informatics and Computing, Indiana University, Bloomington, IN, U.S.A.
}
